Reinforcement \change{L}earning for \change{O}ptions\\on \change{T}arget \change{V}olatility \change{F}unds\thanks{Supported by ISCRA from Cineca, \email{iscra@cineca.it}.}

### 2023-07-03 tex/m2ef/daluiso_nastasi_pallavicini_polo_rl_for_options_on_tvf.tex
start removing corrections

\title{\change{Optimal strategies for options on target volatility funds}\thanks{\change{Our sincere thanks go to Marco Bianchetti and Diego Pierluigi Giovannini of Intesa Sanpaolo Milan, as well as to the Italian computing center Cineca for its support on our numerical simulations. The opinions here expressed are solely those of the authors and do not represent in any way those of their employers.}}}

\titlerunning{\change{Optimal strategies for options on target volatility funds}}

@@

\institute{Financial Engineering, Intesa Sanpaolo Group,\\
Largo Mattioli 3, 20121 Milan, Italy\\
\email{\{Roberto.Daluiso, Andrea.Pallavicini\}@intesasanpaolo.com} \and
\change{Capital Market Technologies, swissQuant Group AG,}\\
\change{Kuttelgasse 7, 8001 Z\"urich, Switzerland}\\
\email{\change{Nastasi@swissquant.com}} \and Financial Engineering,
X-Numeris S.r.l.,\\ Via Turro, 7 , 20127 Milan, Italy\\
\change{\email{Sp.Stefano.Polo@gmail.com}}}

@@

\begin{abstract}
We deal with \remove{the funding costs} \change{a stochastic optimal control problem} rising from hedging the risky securities underlying a target volatility strategy \remove{(TVS)}, a portfolio \remove{of risky assets and a risk-free one dynamically rebalanced in order to keep the} \change{whose asset-allocation is adjusted to maintain the} realized volatility of the portfolio \remove{on} \change{at} a certain level. \change{We consider the point of view of a derivative writer selling an option contract as protection to a portfolio manager on the invested capital.} The uncertainty in the \remove{TVS} risky portfolio composition along with the difference in hedging costs \change{of its} \remove{for each} component\change{s} requires to \remove{solve a control problem to evaluate the option} \change{adjust the protection} price\remove{s} \change{to include these costs in the worst-case scenario for the seller}. We derive an analytical solution of the problem in \remove{the} \change{a} Black and Scholes \remove{(BS)} scenario. Then\change{,} we use Reinforcement Learning \remove{(RL)} techniques to determine the fund composition leading to the \remove{most conservative price} \change{optimal policy} under the local volatility \remove{(LV)} model, for which an {\it a priori} solution is not available. We show how the performances of the \remove{RL agents} \change{numerical solution}  are compatible with those obtained by applying path-wise the \remove{BS} analytical \change{solution previously derived.} \remove{strategy to the TVS dynamics, which therefore appears competitive also in the LV scenario}

@@

\noindent {\bf Keywords.} \change{Stochastic control problem, reinforcement learning, target volatility, option pricing, hedging costs.}

@@

\section{Introduction}
In the recent years portfolio managers \remove{are} \change{were} exposed to very low interest rates and quickly changing market volatilities. An effective solution to control risks under such an environment is given by target volatility strategies (TVSs)\change{,} \remove{(}also known as constant volatility targeting\remove{)}\change{,} which are able to preserve the portfolio at a predetermined level of volatility. A TVS is \change{a strategy for managing} a portfolio of risky assets (typically  equities) and a risk-free \change{one} \remove{asset} dynamically re-balanced with the aim of maintaining the overall portfolio volatility level \remove{closed} \change{close} to some target value. \change{The strategy is designed to achieve a stable level of volatility for the underlying portfolio in any market scenario, and to allow a free selection of the relative allocation weights among the risky assets. }The constant volatility approach can help investors to obtain desired risk exposures over the short and long term and \change{possibly} it increases the risk-adjusted performance of the portfolio.

\remove{These products} \change{Financial products embedding this strategy} were initially offered in the Asian markets, see for instance \remove{the reports of} \cite{Chew2011} and \cite{Xue2012}, which highlight the pros and cons for investors, to be adopted in the following years in many other markets in North America and Europe as depicted in \cite{Morrison2013}. At the present day\change{,} we can observe some new market indices based on the mechanism of the target volatility strategy such as Dow Jones Volatility Control Index, and S\&P 500 Risk Control Index.
In the recent literature\change{,} \remove{TVSs are tested to investigate their performances} \change{TVS-based portfolios are investigated with respect to} their performances in term\change{s} of realized returns, see for instance \cite{Hocquard2013} and \cite{Perchet2016}, and the soundness of the volatility targeting algorithm, as described in \cite{Kim2018}\change{, where the authors propose the use of artificial neural networks for volatility forecasting to enhance the performance of an asset allocation strategy}.

\remove{Moreover, in the present day, in the derivative market new structured financial products that see TVSs as underlying are becoming widely used by practitioners. Those derivative instruments are known as target volatility options (TVOs) have gained great interest in the derivative pricing literature, see in particular} \change{The success of TVS-based products has led to the emergence of derivative contracts, known as target volatility options (TVO), where the TVS itself is used as underlying asset of the contract. In the derivative pricing literature TVOs are reviewed in } \cite{Albeverio2019}, \cite{DiGraziano2012}, \cite{DiPersio2019}, and \cite{Grasselli2016}.

This paper \change{aims to enrich the pricing framework of the TVOs by studying for the first time,} \remove{is the first attempt} to the best of our knowledge, \remove{to study} the funding costs coming from hedging \change{(or simply hedging costs)} the risky assets underlying the target volatility strategy. In particular, we consider the point of view of \remove{a bank} \change{an option writer (for example a bank)} selling a call option to a portfolio manager as protection on the capital invested in a TVS. \change{During her activity the} \remove{The} portfolio manager has the freedom of changing the relative weights of the risky assets during the life of the TVS \change{depending on how the market evolves}. Since \change{the fund manager's decisions cannot be known {\it a priori} and since} the risky assets have different hedging costs, the \remove{bank} \change{option writer} shall adjust the price of the protection to include \remove{them} \change{these costs} in the worst-case scenario, i.e. the most expensive strategy in term of the \remove{financing} \change{hedging} costs. Hence, the pricing problem becomes a continuous dynamical control problem over the risky portfolio composition\change{: the problem of finding the manager's optimal strategy that leads to the maximum protection price}.

In our work\change{,} we provide \remove{to} the reader \change{with} a formal description of the stochastic control problem \change{and we show that it can be solved only numerically considering a general state-dependent dynamics for the risky assets.} \change{However, we prove that} \remove{and most importantly we derive} an analytical solution to the problem \change{exists,} assuming that the risky asset\change{,} dynamics underlying the TVS \change{portfolio}  follow a Black and Scholes (BS) model \cite{BlackScholes1973} and that the derivative contract is a European-style option. \change{As our first contribution, we derive the BS closed solution in two different ways: either applying the Gy\"ongy Lemma or the Hamilton-Jacobi-Bellman equation.}

\change{In the second part of our work we tackle the problem in the general case of a state-dependent dynamics for the risky assets for which only the numerical approach is admissible.}
\remove{Although from a theoretical point of view this solution represents a sub-optimal strategy when dealing with generic dynamics for the risky assets, we show that the BS solution provides a strong baseline as price to practitioners when testing it against numerical methods with different levels of sophistication for solving the control problem}. More precisely we numerically study the problem \remove{in the general case of  a local volatility dynamics \cite{Derman1994}, \cite{Dupire1994} by adopting a Reinforcement Learning approach, in particular an \textit{ad hoc} vanilla direct policy algorithm and the more sophisticated proximal policy optimization technique developed in \cite{Schulman2017}} \change{assuming a local volatility (LV) dynamics \cite{Derman1994}, \cite{Dupire1994} \change{for the risky assets}. The reason for selecting the LV model is its widespread adoption in the industry to value derivatives, especially those related to asset baskets \cite{Gatheral2006}. The LV investigation is based on a Reinforcement Learning approach due to the high dimensionality of the problem we deal with. In particular, we compare the performances of a plain direct policy search gradient-based algorithm \cite{Sutton2018} with those of the more sophisticated proximal policy optimization technique developed in \cite{Schulman2017}. At the end of our study, we show that the solution found in the BS scenario provides a good approximation of the LV solution, which could be favored by practitioners if computational time is valued.}
\\

The paper is organized as follows. In Section \ref{sec:TVS} we introduce more in detail the \remove{manager-bank} contract \change{between the option-writer and the manager} and provide the description of the TVS dynamics in presence of valuation adjustments such as the hedging costs. Then, in Section \ref{sec:Derivative} we introduce the structured class of derivative contracts linked to TVSs, where we describe the arising dynamical control problem for pricing those options. Moreover\change{,} in this section we derive the BS closed solution for European TVOs in two different ways: one applying the Gy\"ongy Lemma and the other \change{through} \remove{by writing} the Hamilton-Jacobi-Bellman equation. In Section \ref{sec:RL} we illustrate how we have applied RL to solve the dynamic control problem, giving a description of the algorithm we have built. We conclude the paper with Section \ref{sec:Numerical_investigations} where we present the numerical results obtained in this work for the Black and Scholes model and the local volatility one.
\\

\remove{A part of this work has been developed during the Master thesis of one of us (SP), where we had the opportunity to collaborate with Marco Bianchetti and Diego Pierluigi Giovannini from Intesa Sanpaolo Milan, that we thank. Moreover we wish to thank the Italian computing centre Cineca, which approved our ISCRA C project and provided us with the high-computing resources of Marconi100 for the numerical simulations of this contribution.
\\

The opinions here expressed are solely those of the authors and do not represent in any way those of their employers.}

\section{Target volatility strategy}\label{sec:TVS}
As mentioned before, this work aims to enrich the TVS pricing literature by studying the aspect related to the funding costs coming from hedging \remove{the risky assets underlying a target volatility portfolio} \change{the underlying risky assets. In the following, we will refer to these costs simply as hedging costs}. \remove{Thus we} \change{We} consider the following scenario: \remove{a bank} \change{an option writer} selling a protection to a portfolio manager who has \remove{his} \change{her} capital invested \change{according to} \remove{in} a TVS. In our case the fund manager has the freedom of changing the relative weights of the risky asset during the life of the TVS; once the allocation strategy is selected then the volatility targeting algorithm rebalances the risky component of the portfolio with the risk-free one in order to keep the overall portfolio volatility close to a target value. Clients investing in the fund pay a running fee for the service of the fund manager and their capital is protected.

The fund manager usually buys from a \remove{bank} \change{counterpart} an option on the TVS to ensure capital protection. For instance, the capital can be protected by buying a put option. In this case, we can write the \change{undiscounted} net asset value (NAV) $A_t$ of the strategy as given by\footnote{Here we neglect discounting factors \change{for sake of clarity}.}
\begin{equation}
    A_t \coloneqq \max\{V_t,K\} = V_t + (K-V_t)^+ \; ,
\end{equation}
where $V_t$ is the price process of the strategy, and $K$ is the guaranteed capital. On the other hand, the fund manager can replicate the payoff by means of the put-call parity by investing the capital in a low-risk asset and buying a call on the strategy
\begin{equation}
    A_t = K + (V_t-K)^+ \; .
\end{equation}

In this way, the TVS is only defined in the two contracts client-fund and fund-\change{option writer} \remove{fund-bank}. The fund manager is not implementing the strategy by trading in the market, and \change{s}he  is not subject to additional costs to access the market. On the other way, the \remove{bank} \change{writer} is paying such costs since she is actively hedging the call option sold to the manager.  The \remove{bank} \change{writer} trading activity implemented to \remove{actively} hedge the option requires funding the collateral procedures of the hedging instruments along with any lending/borrowing fee. \change{We refer to \cite{Gabrielli2020} for a discussion of how to explicitly calculate hedging costs in equity trading.}

We remark that\change{, upon entering into the contract,}  the choices of the manager trading activity \remove{are} \change{can be seen as} stochastic processes since they \change{are not known {\it a priori} and }will depend on the market evolution. Thus, neither the manager strategy nor the \remove{bank financing costs for hedging the option} \change{writer hedging costs} can be written in the fund-\change{writer} \remove{bank} contract\change{: the only contractual elements are the protection strike and maturity, the market in which the manager can trade and the target volatility of the TVS portfolio}. For this reason, the price of a financial product sold by the \remove{bank} \change{writer} is adjusted to include any valuation adjustment due to the trading activity\change{, such as the hedging costs}.

Our aim is to find the most expensive investing strategy from the point of view of \remove{financing} \change{hedging} costs for the \remove{bank} \change{writer} that the manager could choose in the market. In other words, we want to determine the worst-case scenario for the \remove{bank} \change{option-seller}. In the current section, we proceed by defining the price process of the TVS so that we can highlight the impact of valuation adjustments.

\subsection{The strategy \change{p}rice \change{p}rocess}
We work on a filtered probability space $\left(\Omega, \mathcal{F}, \{\mathcal{F}_t\}_{t\geq0}, \mathbb{P}  \right)$ satisfying the usual assumptions for a market model, where $\mathbb{P}$ is the physical probability measure \remove{representing the actual distribution of supply and demand shocks on equities prices}.

We consider a fund trading a basket of $n$ risky securities with price process \change{$S_t = \{S_t^i, \, i=1,\dots,n\}$} \remove{$S_t = (S_t^i, \, i=1,\dots,n)$} funded with a cash account $B_t$ accruing at $r_t$. Any dividend paid by the securities is re-invested in the fund. Here, we assume that the TVS is implemented in continuous time, even if in the practice we can implement the strategy only on a discrete set of dates. We introduce the deflated gain process $\Bar{G}_t^i$ associated with the risky securities as given by
\begin{equation}
    \Bar{G}_t^i \coloneqq \Bar{S}_t^i + \Bar{D}_t^i \; ,
\end{equation}
where we define the deflated price and cumulative dividend processes as 
\begin{equation}
    \bar{S}_t^i \coloneqq \frac{S_t^i}{B_t} \; , \quad \bar{D}^i_t \coloneqq \int_0^t\frac{d\pi_u^i}{B_u} + \int_0^t\frac{d\psi_u^i}{B_u} \; ,
\end{equation}
where $\pi^i_t$ represents the cumulative contractual-coupon process paid by the security, and $\psi_t^i$ represents the cumulative valuation adjustments.
Since fund managers allocating TVS usually rely on equity assets, here we use the results of \cite{Gabrielli2020} that \remove{analyzes} \change{analyze} the valuation adjustments for equity products. We can write 
\begin{equation}
    \psi_t^i \coloneqq \int_0^t S_u^i\mu_u^i du \; ,
\label{eq:XVA_equity}\end{equation}
where we call $\mu_t^i$ cost of carry, which basically represents the hedging costs for the $i$-th security.

Then, we introduce the strategy price process $V_t$, and we define the deflated gain process $\Bar{G}_t^V$ as \remove{given by}
\begin{equation}
    \Bar{G}_t^V \coloneqq \frac{V_t}{B_t} + \int_0^t\frac{V_u\phi_u}{B_u}du \; ,
\end{equation}
where $\phi_t$ are the running fees earned by the fund manager for \remove{his} \change{her} activity. We assume that the strategy is self-financing, so that we can write
\begin{equation}
    d\Bar{G}_t^V = q_t \cdot d\bar{G}_t \; ,
\label{eq:self_financing}\end{equation}
where $q_t^i$ is the quantity invested in the $i$-th security.\footnote{In all formulae we use dot notation for scalar product between vectors, i.e. $a \cdot b = \sum_i a_i b_i$, or between matrix and vector, i.e. $A \cdot b = \sum_j a_{ij}b_j$ or $b \cdot A = \sum_i b_i a_{ij}$.}

Now, in order to prevent arbitrages, we assume the existence of a risk-neutral measure $\mathbb{Q}$ equivalent to $\mathbb{P}$ under which the deflated gain processes of all traded securities are martingales. Under this assumption, we are able to derive the drift conditions on the security price processes, and in turn on the strategy price process\change{, that is}
\begin{equation}
    \forall u >t \quad \bar{G}_t^i = \mathbb{E}_t \left[\bar{G}_u^i\right] \quad\Longrightarrow \quad dS_t^i = r_tS_t^idt-d\pi_t^i-d\psi_t^i + dM_t^i \; ,
\label{eq:risk_neutral}\end{equation}
where $M_t^i$ are martingale\change{s} under $\mathbb{Q}$. If we substitute this expression for the security dynamics into the definition of the strategy we can check that the price process of the strategy is accruing at \change{the following} \remove{a} cash account rate $r_t$ compensated for the fund manager fees
\begin{equation}
    dV_t = V_t(r_t-\phi_t)dt + dM_t^V \; ,
\end{equation}
with $M_t^V$ martingale under $\mathbb{Q}$. Notice that, as expected from non-arbitrage considerations, the coupons paid by each security appear only in the drift of the security price process, but they do not impact the drift of the strategy.

Yet, the strategy priced by $V_t$ cannot be described in the contract between the parties, since Equation~\eqref{eq:self_financing} depends via the security gain processes on the valuation adjustment $\psi_t^i$, which is specific to the investor pricing the strategy. Thus, the TVS defined in the contract will be
\begin{equation}
    d\bar{I}_t \coloneqq q_t \cdot \left(d\bar{S}_t + \frac{d\pi_t}{B_t} \right) - \bar{I}_t\phi_t dt \quad \text{with} \quad I_0 = V_0 \; , 
\label{eq:TVS_first}\end{equation}
leading to the following price process dynamics
\begin{equation}
    dI_t = I_t(r_t-\phi_t)dt -q_t\cdot d\psi_t +dM_t^I \; ,
\end{equation}
with $M_t^I$ martingale under $\mathbb{Q}$. In this case\change{,} we observe that $I_t$ depends explicitly both on the valuation adjustments and on the allocation strategy. Indeed, if we substitute the valuation adjustments with their explicit expression \eqref{eq:XVA_equity}, we get
\begin{equation}
    dI_t = I_t(r_t-\phi_t)dt - q_t \cdot S_t \mu_t dt + dM_t^I \; ,
\end{equation}
where we can see the dependency on the cost of carry $\mu_t$ and on the allocation strategy.

>>>>

	\title{Optimal strategies for options on target volatility funds\thanks{Our sincere thanks go to Marco Bianchetti and Diego Pierluigi Giovannini of Intesa Sanpaolo Milan, as well as to the Italian computing center Cineca for its support on our numerical simulations. The opinions here expressed are solely those of the authors and do not represent in any way those of their employers.}}

	\titlerunning{Optimal strategies for options on target volatility funds}

@@

	\institute{Financial Engineering, Intesa Sanpaolo Group,\\
	Largo Mattioli 3, 20121 Milan, Italy\\
	\email{\{Roberto.Daluiso, Andrea.Pallavicini\}@intesasanpaolo.com} \and
	Capital Market Technologies, swissQuant Group AG,\\
	Kuttelgasse 7, 8001 Z\"urich, Switzerland\\
	\email{Nastasi@swissquant.com} \and Financial Engineering,
	X-Numeris S.r.l.,\\ Via Turro, 7 , 20127 Milan, Italy\\
	\email{Sp.Stefano.Polo@gmail.com}}

@@

	\begin{abstract}
	We deal with a stochastic optimal control problem rising from hedging the risky securities underlying a target volatility strategy, a portfolio whose asset-allocation is adjusted to maintain the realized volatility of the portfolio at a certain level. We consider the point of view of a derivative writer selling an option contract as protection to a portfolio manager on the invested capital. The uncertainty in the risky portfolio composition along with the difference in hedging costs of its components requires to adjust the protection price to include these costs in the worst-case scenario for the seller. We derive an analytical solution of the problem in a Black and Scholes scenario. Then, we use Reinforcement Learning techniques to determine the fund composition leading to the optimal policy under the local volatility model, for which an {\it a priori} solution is not available. We show how the performances of the numerical solution are compatible with those obtained by applying path-wise the analytical solution previously derived.

@@

	\noindent {\bf Keywords.} Stochastic control problem, reinforcement learning, target volatility, option pricing, hedging costs.

@@

	\section{Introduction}
	In the recent years portfolio managers were exposed to very low interest rates and quickly changing market volatilities. An effective solution to control risks under such an environment is given by target volatility strategies (TVSs), also known as constant volatility targeting, which are able to preserve the portfolio at a predetermined level of volatility. A TVS is a strategy for managing a portfolio of risky assets (typically  equities) and a risk-free one dynamically re-balanced with the aim of maintaining the overall portfolio volatility level close to some target value. The strategy is designed to achieve a stable level of volatility for the underlying portfolio in any market scenario, and to allow a free selection of the relative allocation weights among the risky assets. The constant volatility approach can help investors to obtain desired risk exposures over the short and long term and possibly it increases the risk-adjusted performance of the portfolio.

	Financial products embedding this strategy were initially offered in the Asian markets, see for instance \cite{Chew2011} and \cite{Xue2012}, which highlight the pros and cons for investors, to be adopted in the following years in many other markets in North America and Europe as depicted in \cite{Morrison2013}. At the present day, we can observe some new market indices based on the mechanism of the target volatility strategy such as Dow Jones Volatility Control Index, and S\&P 500 Risk Control Index.
	In the recent literature, TVS-based portfolios are investigated with respect to their performances in terms of realized returns, see for instance \cite{Hocquard2013} and \cite{Perchet2016}, and the soundness of the volatility targeting algorithm, as described in \cite{Kim2018}, where the authors propose the use of artificial neural networks for volatility forecasting to enhance the performance of an asset allocation strategy.

	The success of TVS-based products has led to the emergence of derivative contracts, known as target volatility options (TVO), where the TVS itself is used as underlying asset of the contract. In the derivative pricing literature TVOs are reviewed in \cite{Albeverio2019}, \cite{DiGraziano2012}, \cite{DiPersio2019}, and \cite{Grasselli2016}.

	This paper aims to enrich the pricing framework of the TVOs by studying for the first time, to the best of our knowledge, the funding costs coming from hedging (or simply hedging costs) the risky assets underlying the target volatility strategy. In particular, we consider the point of view of an option writer (for example a bank) selling a call option to a portfolio manager as protection on the capital invested in a TVS. During her activity the portfolio manager has the freedom of changing the relative weights of the risky assets during the life of the TVS depending on how the market evolves. Since the fund manager's decisions cannot be known {\it a priori} and since the risky assets have different hedging costs, the option writer shall adjust the price of the protection to include these costs in the worst-case scenario, i.e. the most expensive strategy in term of the hedging costs. Hence, the pricing problem becomes a continuous dynamical control problem over the risky portfolio composition: the problem of finding the manager's optimal strategy that leads to the maximum protection price.

	In our work, we provide the reader with a formal description of the stochastic control problem and we show that it can be solved only numerically considering a general state-dependent dynamics for the risky assets. However, we prove that an analytical solution to the problem exists, assuming that the risky asset, dynamics underlying the TVS portfolio follow a Black and Scholes (BS) model \cite{BlackScholes1973} and that the derivative contract is a European-style option. As our first contribution, we derive the BS closed solution in two different ways: either applying the Gy\"ongy Lemma or the Hamilton-Jacobi-Bellman equation.

	In the second part of our work we tackle the problem in the general case of a state-dependent dynamics for the risky assets for which only the numerical approach is admissible.
	More precisely we numerically study the problem assuming a local volatility (LV) dynamics \cite{Derman1994}, \cite{Dupire1994} for the risky assets. The reason for selecting the LV model is its widespread adoption in the industry to value derivatives, especially those related to asset baskets \cite{Gatheral2006}. The LV investigation is based on a Reinforcement Learning approach due to the high dimensionality of the problem we deal with. In particular, we compare the performances of a plain direct policy search gradient-based algorithm \cite{Sutton2018} with those of the more sophisticated proximal policy optimization technique developed in \cite{Schulman2017}. At the end of our study, we show that the solution found in the BS scenario provides a good approximation of the LV solution, which could be favored by practitioners if computational time is valued.
	\\

	The paper is organized as follows. In Section \ref{sec:TVS} we introduce more in detail the contract between the option-writer and the manager and provide the description of the TVS dynamics in presence of valuation adjustments such as the hedging costs. Then, in Section \ref{sec:Derivative} we introduce the structured class of derivative contracts linked to TVSs, where we describe the arising dynamical control problem for pricing those options. Moreover, in this section we derive the BS closed solution for European TVOs in two different ways: one applying the Gy\"ongy Lemma and the other through the Hamilton-Jacobi-Bellman equation. In Section \ref{sec:RL} we illustrate how we have applied RL to solve the dynamic control problem, giving a description of the algorithm we have built. We conclude the paper with Section \ref{sec:Numerical_investigations} where we present the numerical results obtained in this work for the Black and Scholes model and the local volatility one.

	\section{Target volatility strategy}\label{sec:TVS}
	As mentioned before, this work aims to enrich the TVS pricing literature by studying the aspect related to the funding costs coming from hedging the underlying risky assets. In the following, we will refer to these costs simply as hedging costs. We consider the following scenario: an option writer selling a protection to a portfolio manager who has her capital invested according to a TVS. In our case the fund manager has the freedom of changing the relative weights of the risky asset during the life of the TVS; once the allocation strategy is selected then the volatility targeting algorithm rebalances the risky component of the portfolio with the risk-free one in order to keep the overall portfolio volatility close to a target value. Clients investing in the fund pay a running fee for the service of the fund manager and their capital is protected.

	The fund manager usually buys from a counterpart an option on the TVS to ensure capital protection. For instance, the capital can be protected by buying a put option. In this case, we can write the undiscounted net asset value (NAV) $A_t$ of the strategy as given by\footnote{Here we neglect discounting factors for sake of clarity.}
	\begin{equation}
		A_t \coloneqq \max\{V_t,K\} = V_t + (K-V_t)^+ \; ,
	\end{equation}
	where $V_t$ is the price process of the strategy, and $K$ is the guaranteed capital. On the other hand, the fund manager can replicate the payoff by means of the put-call parity by investing the capital in a low-risk asset and buying a call on the strategy
	\begin{equation}
		A_t = K + (V_t-K)^+ \; .
	\end{equation}

	In this way, the TVS is only defined in the two contracts client-fund and fund-option writer. The fund manager is not implementing the strategy by trading in the market, and she is not subject to additional costs to access the market. On the other way, the writer is paying such costs since she is actively hedging the call option sold to the manager.  The writer trading activity implemented to hedge the option requires funding the collateral procedures of the hedging instruments along with any lending/borrowing fee. We refer to \cite{Gabrielli2020} for a discussion of how to explicitly calculate hedging costs in equity trading.

	We remark that, upon entering into the contract,  the choices of the manager trading activity can be seen as stochastic processes since they are not known {\it a priori} and will depend on the market evolution. Thus, neither the manager strategy nor the writer hedging costs can be written in the fund-writer contract: the only contractual elements are the protection strike and maturity, the market in which the manager can trade and the target volatility of the TVS portfolio. For this reason, the price of a financial product sold by the writer is adjusted to include any valuation adjustment due to the trading activity, such as the hedging costs.

	Our aim is to find the most expensive investing strategy from the point of view of hedging costs for the writer that the manager could choose in the market. In other words, we want to determine the worst-case scenario for the option-seller. In the current section, we proceed by defining the price process of the TVS so that we can highlight the impact of valuation adjustments.

	\subsection{The strategy price process}
	We work on a filtered probability space $\left(\Omega, \mathcal{F}, \{\mathcal{F}_t\}_{t\geq0}, \mathbb{P}  \right)$ satisfying the usual assumptions for a market model, where $\mathbb{P}$ is the physical probability measure \remove{representing the actual distribution of supply and demand shocks on equities prices}.

	We consider a fund trading a basket of $n$ risky securities with price process $S_t = \{S_t^i, \, i=1,\dots,n\}$ funded with a cash account $B_t$ accruing at $r_t$. Any dividend paid by the securities is re-invested in the fund. Here, we assume that the TVS is implemented in continuous time, even if in the practice we can implement the strategy only on a discrete set of dates. We introduce the deflated gain process $\Bar{G}_t^i$ associated with the risky securities as given by
	\begin{equation}
		\Bar{G}_t^i \coloneqq \Bar{S}_t^i + \Bar{D}_t^i \; ,
	\end{equation}
	where we define the deflated price and cumulative dividend processes as 
	\begin{equation}
		\bar{S}_t^i \coloneqq \frac{S_t^i}{B_t} \; , \quad \bar{D}^i_t \coloneqq \int_0^t\frac{d\pi_u^i}{B_u} + \int_0^t\frac{d\psi_u^i}{B_u} \; ,
	\end{equation}
	where $\pi^i_t$ represents the cumulative contractual-coupon process paid by the security, and $\psi_t^i$ represents the cumulative valuation adjustments.
	Since fund managers allocating TVS usually rely on equity assets, here we use the results of \cite{Gabrielli2020} that analyze the valuation adjustments for equity products. We can write 
	\begin{equation}
		\psi_t^i \coloneqq \int_0^t S_u^i\mu_u^i du \; ,
	\label{eq:XVA_equity}\end{equation}
	where we call $\mu_t^i$ cost of carry, which basically represents the hedging costs for the $i$-th security.

	Then, we introduce the strategy price process $V_t$, and we define the deflated gain process $\Bar{G}_t^V$ as
	\begin{equation}
		\Bar{G}_t^V \coloneqq \frac{V_t}{B_t} + \int_0^t\frac{V_u\phi_u}{B_u}du \; ,
	\end{equation}
	where $\phi_t$ are the running fees earned by the fund manager for her activity. We assume that the strategy is self-financing, so that we can write
	\begin{equation}
		d\Bar{G}_t^V = q_t \cdot d\bar{G}_t \; ,
	\label{eq:self_financing}\end{equation}
	where $q_t^i$ is the quantity invested in the $i$-th security.\footnote{In all formulae we use dot notation for scalar product between vectors, i.e. $a \cdot b = \sum_i a_i b_i$, or between matrix and vector, i.e. $A \cdot b = \sum_j a_{ij}b_j$ or $b \cdot A = \sum_i b_i a_{ij}$.}

	Now, in order to prevent arbitrages, we assume the existence of a risk-neutral measure $\mathbb{Q}$ equivalent to $\mathbb{P}$ under which the deflated gain processes of all traded securities are martingales. Under this assumption, we are able to derive the drift conditions on the security price processes, and in turn on the strategy price process, that is
	\begin{equation}
		\forall u >t \quad \bar{G}_t^i = \mathbb{E}_t \left[\bar{G}_u^i\right] \quad\Longrightarrow \quad dS_t^i = r_tS_t^idt-d\pi_t^i-d\psi_t^i + dM_t^i \; ,
	\label{eq:risk_neutral}\end{equation}
	where $M_t^i$ are martingales under $\mathbb{Q}$. If we substitute this expression for the security dynamics into the definition of the strategy we can check that the price process of the strategy is accruing at the following cash account rate $r_t$ compensated for the fund manager fees
	\begin{equation}
		dV_t = V_t(r_t-\phi_t)dt + dM_t^V \; ,
	\end{equation}
	with $M_t^V$ martingale under $\mathbb{Q}$. Notice that, as expected from non-arbitrage considerations, the coupons paid by each security appear only in the drift of the security price process, but they do not impact the drift of the strategy.

	Yet, the strategy priced by $V_t$ cannot be described in the contract between the parties, since Equation~\eqref{eq:self_financing} depends via the security gain processes on the valuation adjustment $\psi_t^i$, which is specific to the investor pricing the strategy. Thus, the TVS defined in the contract will be
	\begin{equation}
		d\bar{I}_t \coloneqq q_t \cdot \left(d\bar{S}_t + \frac{d\pi_t}{B_t} \right) - \bar{I}_t\phi_t dt \quad \text{with} \quad I_0 = V_0 \; , 
	\label{eq:TVS_first}\end{equation}
	leading to the following price process dynamics
	\begin{equation}
		dI_t = I_t(r_t-\phi_t)dt -q_t\cdot d\psi_t +dM_t^I \; ,
	\end{equation}
	with $M_t^I$ martingale under $\mathbb{Q}$. In this case, we observe that $I_t$ depends explicitly both on the valuation adjustments and on the allocation strategy. Indeed, if we substitute the valuation adjustments with their explicit expression \eqref{eq:XVA_equity}, we get
	\begin{equation}
		dI_t = I_t(r_t-\phi_t)dt - q_t \cdot S_t \mu_t dt + dM_t^I \; ,
	\end{equation}
	where we can see the dependency on the cost of carry $\mu_t$ and on the allocation strategy.

	\subsection{The volatility targeting constraint}
	In a typical TVS, the fund manager selects a risky-asset portfolio with a specific time-dependent allocation strategy expressed by means of the vector of relative weights $\alpha_t$, along with a risk-free asset, which we can identify with the bank account $B_t$. In the following, for sake of simplicity in exposition, we consider only total-return securities, namely we set $\pi_t=0$, which means that the security is not paying dividends. Thus we can write Equation~\eqref{eq:TVS_first} as given by
	\begin{equation}
		\frac{dI_t}{I_t}= \omega_t \alpha_t \cdot \frac{dS_t}{S_t} + \left(1-\omega_t  \alpha_t \cdot \mathds{1} \right)\frac{dB_t}{B_t}- \phi_t dt \; ,
	\label{eq:TVS_elegant}\end{equation}
	where $\mathds{1}$ is a $n$-dimensional vector of ones and $\omega_t\in[0,1]$ is determined so that the strategy log-normal volatility is kept constant, namely
	\begin{equation}
			\omega_t: \quad \mathrm{Var}_t[dI_t] = \bar{\sigma}^2I_t^2dt \; ,
	\label{eq:general_tvs_wght}\end{equation}
	where $\Bar{\sigma}$ is the target volatility value.
	In practice, this means that the fund manager will select a risky-portfolio choosing $\alpha_t$ equities from the universe where she can trade, and after that, her choices will be scaled by the automatic target volatility algorithm $\omega_t$ \eqref{eq:general_tvs_wght}.\footnote{We recall that the universe of assets where the manager can trade and the value of $\bar{\sigma}$ are written in the contract.}

	It is possible to derive the expression for $\omega_t$ assuming a generic continuous semi-martingales dynamics under the risk-neutral measure for the underlying securities, so that Equation~\eqref{eq:risk_neutral} can be written as 
	\begin{equation}
		\frac{dS_t^i}{S_t^i} = \left(r_t - \mu_t^i \right)dt + \nu_t^i \cdot dW_t \; ,
	\label{eq:Equity_process}\end{equation}
	where $\nu_t$ is an adapted matrix process ensuring the existence of a solution for the stochastic differential equation \remove{(SDE)} and $W_t$ is a $n$-dimensional vector of Brownian motions under $\mathbb{Q}$. Under these assumptions we can derive an expression for $\omega_t$, and we get\footnote{In all formulae the norm for a vector $a$ is defined as $\|a\|\coloneqq\sqrt{a\cdot a}$.}
	\begin{equation}
		\omega_t = \frac{\Bar{\sigma}}{\norm{ \alpha_t\cdot \nu_t }} \; .
	\end{equation}
	Hence, putting this last result in the dynamics of $I_t$ we obtain

	\begin{equation}
		\frac{dI_t}{I_t} = \left(r_t -  \phi_t     - \frac{\bar{\sigma} \alpha_t}{\norm {\alpha_t \cdot \nu_t }}  \cdot \mu_t \right)dt+ \frac{\bar{\sigma}\alpha_t }{\norm{ \alpha_t \cdot \nu_t }} \cdot \nu_t \cdot dW_t \; ,
	\label{eq:TVS_last}\end{equation}
	where we can see, as expected, that the strategy grows at the risk-free rate but for the valuation adjustments, given by the hedging costs expressed by the term proportional to $\mu_t$ in \eqref{eq:TVS_last}, and the fees, given by the term $\phi_t$ in \eqref{eq:TVS_last}.

	We highlight that, to derive the dynamics expressed in Equation~\eqref{eq:TVS_last}, we have not made any assumptions on the risky allocation strategy; thus all this argument is valid for any constraints on the process $\alpha_t$ as, for instance, the case of contracts in which the fund manager is restricted to holding only long positions meaning that $\alpha_t^i\geq0$ $\forall i = 1,\dots,n$, or situations where the combined total of long and short trades must be capped at a specific contractual amount.

	\section{Derivative pricing: target volatility options}\label{sec:Derivative}
	In this section, we analyze TVO contracts, namely contracts linked to the TVS described previously. In particular, we will focus on European style options, and we will show that under appropriate assumptions it is possible to find a closed form solution for the optimal allocation strategy which maximizes the contract price.
